\textls[-0]{\thetitle}

### 2023-03-06 canonicitymodel.tex
Remove all mentioning about Agda Make sure proof stands alone in latex form.

Like most logical relation proof,  we interpret each judgement and prove compatibility lemma.

% The proof can be found in appendix. 
The intuition of the model is similar to that of the consistency model---use the canonicity model of sigma type (from the earlier work) for linkage type and using Agda's inductive facility to justify our W-type.

>>>>

Like most logical relation proof,  we interpret each judgement, inductively interpret each syntax piece and prove compatibility lemma. We are working on an intrinsic setting thus even we omit context for brevity, the syntax piece is still well-typed. We only specify part of the logical relation proof for MLTT part. For the complete version, please refer to \citet{kaposi2019gluing, coquand2018canonicity,sterling2019algebraic}.

\begin{align*}
  \denotesC{\goodCtx{\Gm}{i}} & \text{ is a Set of closed substitution} \goodSub{\cdot}{\_}{\Gm} \\
  &\text{and we define } \goodCtxS{\Gm}{i} :\iff \denotesC{\goodCtx{\Gm}{i}} \text{ is defined} \\
  \denotesC{\goodType{\Gm}{T}{}} & \text{ is a function maps to Set s.t.} \\
  & \text{for arbitrary } \gm \in \denotesC{\goodCtx{\Gm}{}}, \denotesC{\goodType{\Gm}{T}{}}(\gm) \text{ is a Set of closed terms } \goodTerm{\cdot}{\_}{\sub{T}{\gm}} \\ 
  &\text{and we define } \goodTypeS{\Gm}{T}{i} : \iff \denotesC{\goodType{\Gm}{T}{i}} \text{ is defined } \\ 
  \denotesC{\goodSub{\Gm}{\gm}{\Delta}} & \text{ is a function}: \denotesC{\goodCtx{\Gm}{i}} \to \denotesC{\goodCtx{\Delta}{i}} \text{ s.t. } \denotesC{\goodSub{\Gm}{\gm}{\Delta}}(\sigma) \coloneqq \SubstComp{\sigma}{\gm} \\
  &\text{and we define } \goodSubC{\Gm}{\gm}{\Delta} :\iff \denotesC{\goodSub{\Gm}{\gm}{\Delta}} \text{ is defined} \\
  \denotesC{\goodTerm{\Gm}{t}{T}} & \text{ is a dependent function}: \prod_{\gm \in \denotesC{\goodCtx{\Gm}{i}}}\denotesC{\goodType{\Gm}{T}{}}(\gm)  \text{ s.t. } \denotesC{\goodTerm{\Gm}{t}{T}}(\gm) \coloneqq \sub{t}{\gm} \\
  \denotesC{\goodType{\Gm}{\top}{}}(\gm) &= \{t : t \equiv \unit \} \\
  \denotesC{\goodType{\Gm}{\bot}{}}(\gm) &= \emptyset \\
  \denotesC{\goodType{\Gm}{\cB}{}}(\gm) &= \{t : t \equiv \true \text{ or } t \equiv\false \} \\
  \denotesC{\goodType{\Gm}{\TyId{a}{b}}{}}(\gm) &= \{t : t \equiv \eqrefl{\sub{a}{\gm}} \} \text{ when } \sub{a}{\gm} \equiv \sub{b}{\gm} \\ 
  &= \emptyset \text{ otherwise } \\ 
  \denotesC{\goodType{\Gm}{\TyPi{A}{B}}{}} &= \\
  \denotesC{\goodType{\Gm}{\TySigma{A}{B}}{}} &= \\
  \denotesC{\goodCtx{\cdot}{}} &= \{\SubstEmp\} \text{  the singleton set with identity substitution} \\ 
  \denotesC{\goodCtx{\Gm, T}{}} &= \{ (\gamma , t) : \gamma \in \denotesC{\goodCtx{\Gm}{}}, t \in \denotesC{\goodType{\cdot}{\sub{T}{\gm}}{}}  \} \\
  \denotesC{\goodTerm{\Gm}{\lam{t}}{\TyPi{A}{B}}} &= \\
  \denotesC{\goodTerm{\Gm}{\app{t}}{B}} &= \\
  \denotesC{\goodTerm{\Gm}{\pair{a}{b}}{\TySigma{A}{B}}} &= \\
  \denotesC{\goodTerm{\Gm}{\pair{a}{b}}{\TySigma{A}{B}}} &=
\end{align*}

Then we extend the above model to \TT , we still start with the judgement.
The intuition of the model is similar to that of the consistency model---use the canonicity model of sigma type (from the earlier work) for linkage type and using Agda's inductive facility to justify our W-type.

Now that we construct the above model, we can map an arbitrary closed term $\goodTerm{\cdot}{t}{\cB}$ to get the result $\denotesC{\goodTerm{\cdot}{t}{\cB}}(\SubstEmp) = \sub{t}{\SubstEmp} \in \sub{\cB}{\SubstEmp} = \{\true, \false\}$, Thus $t \equiv \true \text{ or } t \equiv\false$.

### 2023-03-06 metatheory2.tex
Remove all mentioning about Agda Make sure proof stands alone in latex form.

\subsection{Warm Up: Review Declarative MLTT}
We begin with a review of MLTT as \TT can be roughly considered as MLTT with linkages.
For our syntax, we work in an intrinsic-typed setting, so there is no un-typed preterms 
(i.e. every terms are well-typed by construction). We introduce judgemental equality $\equiv$
for derivations (of each judgements). In other words, we will have judgemental equality between terms, 
contexts and explicits substitutions. 
We will make sure all the introduced models and proofs respecting judgemental equality.

@@

% Copy and Paste Intuition of MLTT from other places to here
\subsection{\TT : an MLTT variant with Linkages}
Compared to MLTT, \TT has 3 more judgements about signatures and linkage transformers.

>>>>

\subsection{Warm Up: Review Declarative Syntax for MLTT}
We begin with a review of MLTT as \TT can be roughly considered as MLTT with linkages.
For our syntax, we work in an intrinsic-typed setting, so there is no un-typed preterms appearing anywhere. We introduce judgemental equality ($\equiv$)
for derivations (of all kinds of judgements). In other words, we will have judgemental equality between terms, 
contexts and explicits substitutions. 
We will make sure all the introduced models and proofs respecting judgemental equality. In other words, we will consider our syntax as the result of taking quotient by these judgemental equality.

@@

% Copy and Paste Intuition of MLTT from other places to here
\subsection{Declarative Syntax for \TT : an MLTT variant with Linkages}
Compared to MLTT, \TT has 3 more judgements about signatures and linkage transformers.
